---
title: "HeartDisease"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Choose an appropriate model type
The model type chosen is a logistic regression model as we are looking to predict a binary value

```{r}
library(caret)
library(e1071)
heartData <- read.csv("HDdata.csv")
summary(heartData)
```

###In your data are there
a. NAs?
Yes there are 10 NAs in the age variable

b. categorical values
Yes cp and restecg are categorical values 

c. binary values
Yes sex, fbs, exang and num are binary values

d. numeric values
age, trestbps, chol, thalach and oldpeak are numeric values


```{r}
#pre-processing
heartData$sex <- as.factor(heartData$sex)
heartData$cp <- as.factor(heartData$cp)
heartData$fbs <- as.factor(heartData$fbs)
heartData$restecg <- as.factor(heartData$restecg)
heartData$exang <- as.factor(heartData$exang)
heartData$num <- as.factor(heartData$num)
sum(is.na(heartData))
#There are some na value
heartData <- na.omit(heartData)

```


###Divide you data into a training and test set
```{r}
set.seed(150)
partition <- createDataPartition(y = heartData$num, p = 0.7, list=F)
trainingdata = heartData[partition, ]
testdata = heartData[-partition, ]
```


###Fit a Linear or logistic regression model on the training set and predict using the test set
```{r}
heartlogreg = glm(num ~., data = trainingdata, family = binomial(link='logit'))
```

###Use your test set to assess the accuracy of the model
Using a prediction threshold of 0.5

```{r}
heartlogregPred <- ifelse(predict(heartlogreg, testdata, type="response") > 0.5, 1, 0)
```

Construct a confusion matrix

```{r}
result_table <- table(predicted = heartlogregPred, actual = testdata$num)
result_table
heartlogregConfusionM = confusionMatrix(result_table)
heartlogregConfusionM
```
Claculate the accuracy, PPV, NPV, Sensitivity and Specificty. 

Accuracy is 0.7614

Sensitivity is 0.7872

Specificity is 0.7317

PPV is 0.7708

NPV is 0.7500
